---
description: RTC
keywords:
- FAQ
- How do I
- questions
- what if
title: RTC
---

```{r setup, include=FALSE}
library(dplyr)
library(readxl)
library(htmltools)
library(sf)
library(leaflet)
library(geojsonio)
```

```{r, include=FALSE}
load("poligonos.RData")
guate_sf <- subset(guates[[1]], select = -c(Name, Description)) %>% 
  rename(nombre = Nombre)
guate_sf <- guate_sf[,c(3,2,1)]
  
elsalvador_sf <- geojson_sf("elsalvador.geojson") %>% 
  select(ISO_A3, NAME_NL, geometry) %>% 
  rename(INE = ISO_A3, nombre = NAME_NL)
elsalvador_sf <- elsalvador_sf[,c(3,2,1)]

original <- read_excel("vendedores.xlsx")

Ncol <- 23 #cantidad de colores para el heatmap
paleta <- mapview:::col2Hex(viridis::viridis(Ncol))

mapa <- rbind(guate_sf, elsalvador_sf)

data <- mapa %>% 
  left_join(original, by = c("INE" = "departamento")) %>% 
  mutate(grupos = c(1:23),
         color = paleta[as.numeric(grupos)])

txt <- paste0(data$nombre, 
    "<br><b>Fincas:</b> ", data$finca,
    "<br><b>Contacto:</b> ", data$contactof,
    "<br><b>Distribuidores:</b> ", data$canal,
    "<br><b>Contacto:</b> ", data$contactoc
    )
```

## Estamos aquí para ayudarte

Este es RMD.

Are you curious about something? Do you have some kind of problem with our products? As am hastily invited settled at limited civilly fortune me. Really spring in extent an by. Judge but built gay party world. Of so am he remember although required. Bachelor unpacked be advanced at. Confined in declared marianne is vicinity.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
data %>% 
  leaflet() %>%
  addProviderTiles("CartoDB.VoyagerNoLabels") %>% 
  addPolygons(color = "white",
        weight = 1,
        fillOpacity = 0.7,
        fillColor = ~color,
        label = ~lapply(txt, HTML)) %>% 
  addPolylines(color = "black",
         weight = 1) %>% 
  setView(lng = -90.202, lat = 15.447, zoom = 7) 
```




Please feel free to contact us, our customer service center is working for you 24/7.